\documentclass[12pt,letterpaper]{article}
\input{../../preamble}
\usepackage{fullpage}
\usepackage{multicol}
\everymath{\displaystyle}

\begin{document}
\flushleft
\begin{multicols}{2}

\begin{large}\textbf{Math 2603 Exam 2 \\
Wed 24 Sep 2014}\end{large}

\hfill\textbf{Name:  }\underline{\hspace{35ex}} %KEY\hspace{17ex}} 
\\
\vspace{.5in}

\end{multicols}

\pagestyle{empty}

\vspace{4pc}

\begin{center}\LARGE Discrete Math

Exam 2 (Ch. 3-6 as we have covered) \end{center}

\vspace{2pc}
Please provide the following data:

\vspace{2pc}
Drill Time: \underline{\hspace{40ex}}

\vspace{2pc}
Student ID: \underline{\hspace{40ex}}

\vspace{3pc}
{\bf Exam Instructions:} You have 50 minutes to complete this exam.  One $3\times 5$ inch notecard is allowed.  No graphing calculators.  No programmable calculators.  No phones, iDevices, computers, etc.  If you finish early then you may leave, UNLESS there are less than 5 minutes of class left.  To prevent disruption, if you finish with less than 5 minutes of class remaining then please stay seated and quiet.

\vspace{5pc}
Your signature below indicates that you have read this page and agree to follow the Academic Honesty Policies of the University of Arkansas.  

\vspace{3pc}
Signature: \underline{\hspace{80ex}}

\vfill
\begin{flushright}\Large Good luck!\end{flushright}

\begin{enumerate}

% % % % %
\newpage
\item Determine which of the following are functions.  If they are functions decide if they are one-to-one, onto, or both.  
\begin{enumerate}
\item $f:\mathbb R\to\mathbb R$, given by $f(x)=4x-5$.

\vspace{10pc}
\item $R=\left\{(a,y),(b,z),(c,x),(d,x)\right\}\subset\{a,b,c,d\}\times\{x,y,z\}$

\vspace{10pc}
\end{enumerate}

\item Find an explicit formula for the $n$th term of each of the following sequences.  You must state where your indices $n$ start.
\begin{enumerate}

\vspace{1pc}
\item $s=\left\{\frac{1}{4},\,\frac{2}{9},\,\frac{3}{16},\,\frac{4}{25},\,\frac{5}{36},\,\frac{6}{49},\,\dots\right\}$

\vspace{10pc}
\item $t=\left\{0,\,\frac{-1}{2},\,\frac{2}{3},\,\frac{-3}{4},\,\frac{4}{5},\,\frac{-5}{6},\,\frac{6}{7},\,\dots\right\}$
\end{enumerate}

% % % % %
\newpage
\item Suppose $R$ is a relation on a set $X$.  Write down the following definitions:
\begin{enumerate}

\vspace{1pc}
\item $R$ is \emph{reflexive} means

\vspace{5pc} 
\item $R$ is \emph{symmetric} means

\vspace{5pc} 
\item $R$ is \emph{antisymmetric} means

\vspace{5pc}
\item $R$ is \emph{transitive} means

\vspace{5pc}
\item $R$ is an \emph{equivalence relation} means

\vspace{5pc}
\item $R$ is a \emph{partial order} means
\end{enumerate}

% % % % %
\newpage
\item Define the relation $R$ on $\Z$ by $mRn$ if and only if $3\,|\,(m^2-n^2)$.  Which of the properties from Problem 3 does $R$ satisfy?  Give justification (proof or counterexample) for each of the items (a)-(f) from Problem 3.

% % % % %
\newpage
\item Prove that for the Fibonacci sequence ($f_1=1,\,f_2=1,\dots$)
\[\sum_{i=1}^nf_i^2=f_nf_{n+1}.\]

% % % % %
\newpage
\item A student council consists of 16 students, 5 of whom are men and 11 of whom are women.
\begin{enumerate}

\vspace{1pc}
\item In how many ways can a committee of 5 be selected from the membership of the council?

\vspace{10pc}
\item How many committees of 5 contain at least one man?

\vspace{10pc} 
\item Suppose the council has 2 freshmen, 4 sophomores, 6 juniors, and 4 seniors.  How many committees of 8 contain exactly 2 representatives from each class?  
\end{enumerate}

% % % % %
\newpage
\item {\bf cHaLlEnGe PrObLeM} The sequence of \emph{Catalan numbers} is defined as
\[C_n=\frac{1}{n+1}\binom{2n}{n}\]
for each $n\in\Z_{\geq 1}$.
\begin{enumerate}
\item Prove that $C_n=\binom{2n}{n}-\binom{2n}{n+1}$.  Hint: Use the following Lemma (and prove it).

\begin{lem*} For all nonnegative integers $n$ and $r$ with $r+1\leq n$, 
\[\binom{n}{r+1}=\frac{n-r}{r+1}\binom{n}{r}.\]
\end{lem*} 

\vspace{25pc}
\item Find the first 6 Catalan numbers.
\end{enumerate} 

% % % % %
\newpage
\item {\bf EXTRA CREDIT} Find integers $s,t$ such that 
\[\gcd(825,315)=825s+315t.\]

\end{enumerate}
\end{document}