\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{pstricks, pst-node, pst-plot}

\newcommand{\ds}{\displaystyle}
\newcommand{\bv}{\mathbf}
\newcommand{\lv}{\langle}
\newcommand{\rv}{\rangle}

\begin{document}
\flushleft
\begin{multicols}{2}


\begin{large}\textbf{Math 115 Quiz 2: $\oint $ 1.6-1.8, 2.1 \\
Mon 27 September 2010}\end{large}

\textbf{Name:  }\underline{\hspace{35ex}}

\vspace{.5in}

\end{multicols}

\pagestyle{empty}


\flushleft

You have 15 minutes to complete this quiz.  Calculators are OK.  Eyes on your own paper and good luck!

\begin{enumerate}
\item  \textbf{Definitions/Concepts.} (1 pt each) Suppose that $\lim_{x\rightarrow 3}f(x)=7$.  Are the following statements true or false?  If a statement is true, explain how you know.  If a statement is false, give a counterexample.
\begin{enumerate} 
\item $\lim_{x\rightarrow 3}\left(xf(x)\right)=21$.  

\vspace{3pc}
\item If $g(3)=4$, then $\lim_{x\rightarrow 3}\left(f(x)+g(x)\right)=28$.

\vspace{3pc}
\end{enumerate}

\item \textbf{Questions/Problems.} A ball is tossed into the air from a bridge, and its height, $y$ (in feet), above the ground $t$ seconds after it is thrown is given by 
\[y=f(t)=-16t^2+50t+36.\]
\begin{enumerate}
\item (1 pt) How high above the ground is the bridge? 

\vspace{2pc}
\item (1 pt) What is the average velocity of the ball for the first second?

\vspace{2pc}
\item (1 pt) Approximate the velocity of the ball at $t=1$ second.

\vspace{2pc}
\item (2 pts) Graph $f$, and determine the maximum height the ball reaches.  What is the velocity at the time the ball is at its peak?

\vspace{10pc}
\item (1 pt) Use the graph to decide at what time, $t$, the ball reaches its maximum height.

\vspace{2pc}
\end{enumerate}

\item \textbf{Computations/Algebra.} (1 pt each) 
\begin{enumerate} 
\item Find $k$ so that the following function is continuous on any interval:
\[f(x)=\left\{\begin{array}{ll}
               kx & x\leq 3 \\
               5 & 3<x 
              \end{array}\right.\]
\vspace{3pc}
\item Find $k$ so that the following function is continuous on any interval:
\[f(x)=\left\{\begin{array}{ll}
               kx & 0\leq x< 3 \\
               3x^2 & 2\leq x 
              \end{array}\right.\]
\vspace{3pc}
\end{enumerate}

\end{enumerate}

\end{document}


