\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{pstricks, pst-node, pst-plot}

\newcommand{\ds}{\displaystyle}
\newcommand{\bv}{\mathbf}
\newcommand{\lv}{\langle}
\newcommand{\rv}{\rangle}

\begin{document}
\flushleft
\begin{multicols}{2}


\begin{large}\textbf{Math 115 Quiz 8: $\oint $ 4.3, 4.4 Optimization \\
Mon 15 November 2010}\end{large}

\textbf{Name:  }\underline{\hspace{35ex}}

\vspace{.5in}

\end{multicols}

\pagestyle{empty}

\flushleft

You have 30 minutes to complete this quiz.  Make your variables clear and
consistent (so if you want to say, for example, $\frac{dy}{dx}$, you should also
mention $y=f(x)$, or ``$y$ is a function of $x$'').  Calculators are OK.  

\begin{enumerate}
\item \textbf{Definitions/Concepts.} (1 pt each)
\begin{enumerate}
 \item Give an example of a family of functions, $f(x)$, depending on a parameter $a$, such that each member of the family has exactly one critical point.

\vspace{3pc}
\item TRUE or FALSE: If the radius of a circle is increasing at a constant rate, then so is the area.
\end{enumerate}

\vspace{1pc}
\item \textbf{Questions/Problems.}  Verify your extrema using either a well-labeled graph or the 2nd derivative.
\begin{enumerate}
 \item (2pts) What point(s) on the graph of $y=\frac{1}{x^2}$ is closest to
$(0,0)$?

\vspace{10pc}
\item (3 pts) I have a square piece of sheet metal, 1 meter on a
side. I plan to cut
equal squares from the four corners and fold up the
sides to make a box (with no
top). How big
should the cut-off squares be in order to maximize the
volume of the
box? 
\end{enumerate}

\vspace{10pc}
\begin{flushright}
 turn over $\rightarrow $
\end{flushright}

\pagebreak
\item \textbf{Computations/Algebra.} (1 pt each) Find the critical points.
\begin{enumerate}
\item $f(x)=(x-a)^2+b$

\vspace{5pc}
\item $g(y)=y^3-ay^2+b$

\vspace{5pc}
\item $h(z)=az(z-b)^2$

\vspace{5pc}
\end{enumerate}

\end{enumerate}
----------------------------------------------------------------------------------------

\vspace{1pc}
\noindent \textbf{ChAlLeNgE PrObLeM:}  Give an example of a function $f$ which satisfies the following.  If no such function exists, say why.  Assume $f''$ exists everywhere.  
\[f(x)f'(x)f''(x)f'''(x)<0 \text{ for all }x\]
\end{document}


