\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{pstricks, pst-node, pst-plot}

\newcommand{\ds}{\displaystyle}
\newcommand{\bv}{\mathbf}
\newcommand{\lv}{\langle}
\newcommand{\rv}{\rangle}

\begin{document}
\flushleft
\begin{multicols}{2}


\begin{large}\textbf{Math 115 Quiz 0: Student Guide \\
Mon 13 September 2010}\end{large}

\textbf{Name:  }\underline{\hspace{35ex}}

\vspace{.5in}

\end{multicols}

\pagestyle{empty}


\flushleft

Decide whether each of the statements below is \emph{True} or \emph{False}.  Write the entire word \emph{True} or \emph{False}.  If the statement is false, briefly explain why.  


\begin{enumerate}
\item  Math 115 is graded on a normal 10-point scale, that is 90-100=A, 80-90=B, etc.  

\vspace{.5pc}
False.  The level of difficulty of exams will be considered.

\item  In general, a student should expect to do well in this course if he/she completes all assignments, reads each section before class, and puts in 3-4 hours of study time a week.

\vspace{.5pc}
False.  The faculty at the University of Michigan expects you to study a minimum of two hours outside class for each credit hour, which means that we expect you to spend at least eight hours a week outside of class working on mathematics.

\item In-class work (i.e., team homework and quizzes) accounts for 40\% of your overall course grade.

\vspace{.5pc}
False.  Your instructor will decide how the section component is determined for your particular section and grade the section work.  If, at the end of the term, your rankings on the section component and uniform component differ significantly from one another, your course grade will be examined to see if an adjustment should be made.

\item Each member of the team should submit his/her own version of the solutions for the team homework every week.

\vspace{.5pc}
False.  The scribe is responsible for writing up the single final version of the homework to be handed in.  This is the only set of solutions which will be accepted or graded.

\item If you do not participate in team homework and quizzes, your course grade will be based solely on your exam scores and web homework.

\vspace{.5pc}
False.  Each member of the group will receive the same grade as long as they work with the team.  Students who do NOT participate will receive a zero.

\item If you do not complete a WebHW assignment by the deadline, you can finish it within the following day for partial credit.

\vspace{.5pc}
False.  It's not true.  (I couldn't find anywhere in the Student Guide where this was specifically addressed, but everyone must do the WebHW by the deadline to get credit.)

\item  If you are trying hard in the course and completing all of the work, but your in-class grades are lower than your uniform exam grades, your course grade can be lowered by a full letter grade.

\vspace{.5pc}
False.  If you have participated in section activities but your section component is significantly lower than your uniform grade, your course grade my be lowered by one third of a letter grade.  Students who have not seriously attempted to contribute to the section component of the course (i.e., quizzes, team homework, etc.) may have their final course grade lowered by up to a \emph{full} letter grade.

\item  At the end of the semester, every section of Math 115 will have the same number of A's, B's, etc.

\vspace{.5pc}
Course policy is that a section's average final letter gradde cannot differ too much from that section's average baseline letter grades.  This means that the better your entire section does on the uniform exams, the higher average letter grade your instructor can assign in your section.

\end{enumerate}
\end{document}


