\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{pstricks, pst-node, pst-plot}

\newcommand{\ds}{\displaystyle}
\newcommand{\bv}{\mathbf}
\newcommand{\lv}{\langle}
\newcommand{\rv}{\rangle}

\begin{document}
\flushleft
\begin{multicols}{2}


\begin{large}\textbf{Math 115 Quiz 0: Student Guide \\
Mon 13 September 2010}\end{large}

\textbf{Name:  }\underline{\hspace{35ex}}

\vspace{.5in}

\end{multicols}

\pagestyle{empty}


\flushleft

Decide whether each of the statements below is \emph{True} or \emph{False}.  Write the entire word \emph{True} or \emph{False}.  If the statement is false, briefly explain why.  


\begin{enumerate}
\item  Math 115 is graded on a normal 10-point scale, that is 90-100=A, 80-90=B, etc.  
\vfill
\item  In general, a student should expect to do well in this course if he/she completes all assignments, reads each section before class, and puts in 3-4 hours of study time a week.
\vfill
\item In-class work (i.e., team homework and quizzes) accounts for 40\% of your overall course grade.
\vfill
\item Each member of the team should submit his/her own version of the solutions for the team homework every week.
\vfill

\item If you do not participate in team homework and quizzes, your course grade will be based solely on your exam scores and web homework.
\vfill

\item If you do not complete a WebHW assignment by the deadline, you can finish it within the following day for partial credit.
\vfill
\item  If you are trying hard in the course and completing all of the work, but your in-class grades are lower than your uniform exam grades, your course grade can be lowered  by a full letter grade.
\vfill
\item  At the end of the semester, every section of Math 115 will have the same number of A's, B's, etc.

\end{enumerate}
\end{document}


