\documentclass[margin,line,pifont,palatino,courier]{res}

\usepackage{pifont}
\usepackage[latin1] { inputenc}
\usepackage{dtklogos}
\usepackage{supertabular}

\textheight=9.0in
%\itemsep=0in
%\parsep=0in
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\cfoot{}
%\lfoot{\textit{\footnotesize Research Statement}}
\rfoot{{\footnotesize Syllabus, Discrete Mathematics, \thepage}}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Math 2603 -- Discrete Mathematics \hspace{0.42\textwidth} Fall 2014 \newline
{\small Last updated: \today} \vspace{.1in}}

\begin{resume}

\section{\sc Instructor Information}

\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2in}}
Ashley K. Wheeler & Office: SCEN 356 \\
Visiting Assistant Professor & Email: ashleykw@uark.edu \\
Department of Mathematical Sciences & 
\end{tabular}

%%%
\section{\sc Webpage}
\verb+comp.uark.edu/~ashleykw/DiscreteF2014/2603f14.html+

%%%
\section{\sc Office Hours}
TBA, or by appointment

%%%
\section{\sc Prerequisites}
Students must have successfully completed at least Calculus I with a C or better.  If you have any doubts about your placement, please see your instructor immediately.

%%%
\section{\sc Place and Time} Physics 133

%%%
\section{\sc Text} \emph{Discrete Mathematics, Seventh Edition}, by Richard Johnsonbaugh  (Pearson) 

\vspace{-0.25pc}
%%%
\section{\sc Calculator Policy} Sliderules are permitted, but not required.  No graphing calculators.

%%%
\section{\sc Decorum} All electronic devices including cell phones, iPods, laptops, etc., will not be allowed in classes nor on the desks during exams, including the final.  These items must be turned off and secured in the student's possession during all class and exam times.  Any use of these items in lecture should be cleared with the instructor first.

%%%
\section{\sc Grading} Grades are determined based on points as follows:

\begin{supertabular}{@{}ll}
Three Exams at 100 points each & 300 points \\
Final Exam: Monday, Dec 15 (8-10a) & 200 points \\
Quizzes: Best 10 out of 13ish & 150 points \\
 & {\bf TOTAL: 650 points} \\
\end{supertabular}

The general guidelines for letter grades are as follows:

\begin{tabular}{c c c c c}
A: 90\%-100\% & B: 80\%-89\% & C: 65\%-79\% & D: 50\%-64\% & F: 49\% and below
\end{tabular}

I reserve the right to scale the final totals, but any scaling will be in your favor.  That is to say, you might get an A with an 88\%, but you will not get a B with 90\% or better! {\bf Please keep up with your scores on graded work.  You should be able to determine your standing at any time with regard to grades.}

%%%
\section{\sc Attendance and Participation}

You should feel comfortable in asking questions during lecture.  You are certainly welcome to see me during office times or appointments to ask or discuss material.  Please avail yourself of the opportunities.  Attendance will be monitored on a daily basis.  If you miss a class, it is your responsibility to determine what we did in class that day and to be prepared for the next class meeting.  Any graded work during class time that day cannot be made up due to missing class without advanced approval.  I reserve the right to lower your grade by one letter if unexcused absences exceed 6 including drill on Friday.
 
%\newpage

%%%
\section{\sc Accommodations} Under University policy and federal and state law, students with documented disabilities are entitled to reasonable accommodations to ensure the student has an equal opportunity to perform in class.  If any member of the class has such a disability and needs special academic accommodations, please report to the Center for Educational Access (CEA).  Reasonable accommodations may be arranged after CEA has verified your disability.  Do not hesitate to contact me if any assistance is needed in the process.

%%%
\section{\sc Inclement Weather Policy} In the event of inclement weather, the instructor will make every effort to hold class.  If you feel that your situation for attending class is too risky, then contact your instructor by email, if possibile.  If the University is officially closed, then class is cancelled.  We will set reasonable make-up times for exams based on the circumstances and will notify students in class of changes.

%\vspace{-1pc}
%%%
\section{\sc Disclaimer} WE RESERVE THE RIGHT TO MAKE CHANGES TO THE DAILY SCHEDULE DURING THE SEMESTER.  If changes are made, you will be notified of the changes in class as we proceed.

%%%
\section{\sc Academic \\ Honesty Policy} {\bf Refer to the University of Arkansas Policy on Academic Honesty.}

\end{resume}
\end{document}
