\documentclass[11pt,letterpaper]{article}
\input{G:/Dropbox/Math/preamble}
\usepackage{fullpage}
\usepackage{multicol}

\begin{document}
\flushleft
\begin{multicols}{2}

\begin{large}\textbf{Math 2554 Quiz 6: $\oint $ 3.5-3.7 \\
Tues 7 Oct 2014}\end{large}

\hfill\textbf{Name:  }\underline{\hspace{40ex}} %KEY\hspace{17ex}}

\vspace{.5in}

\end{multicols}

\pagestyle{empty}

\flushleft

You have 20 minutes to complete this quiz.  Eyes on your own paper and good luck!

\begin{enumerate}
\item  \textbf{Definitions/Concepts.} \emph{(none this week)}

% % % % %
%\vspace{0.5pc}
\item \textbf{Questions/Problems.} 
	\begin{enumerate}
	\item Find an equation of the line tangent to the curve $x^2+xy-y^3=7$ at the point $(3,2)$.	

	\vspace{15pc}
	\item {\bf A stone thrown vertically}  Suppose a stone is thrown vertically upward from the edge of a cliff with an initial velocity of 64 ft/s from a height of 32 ft above the ground.  The height $s$ (in feet) of the stone above the ground $t$ seconds after it is thrown is 
	\[s=-16t^2+64t+32.\]
		\begin{enumerate}[(i)]
		\item Determine the velocity $v$ of the stone after $t$ seconds.

\vfill
\hfill {\bf\Large MORE ON THE NEXT PAGE $\to$}

\newpage		
		
		\item When does the stone reach its highest point?
		
		\vspace{10pc}
		\item What is the height of the stone at the highest point?
		
		\vspace{5pc}
		\item When does the stone strike the ground?
		
		\vspace{5pc}
		\item With what velocity does the stone strike the ground?
		
		\vspace{5pc}
		\end{enumerate}
	\end{enumerate}	

% % % % %
\vspace{1pc}
\item \textbf{Computations/Algebra.} Use the Chain Rule to differentiate 
	\begin{enumerate}
	\item $(6x^3+3x+1)^{10}$
	
	\vspace{10pc}
	\item $e^{x^3}$
	\end{enumerate}

\end{enumerate}

%\vspace{30pc}
% % % % %
%{\bf ChAlLeNgE pRoBlEm} \emph{(worth no credit)} Give a nonlinear function $f(x)$ whose tangent at $x=-2$ has slope $3$.

\end{document}