\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{pstricks, pst-node, pst-plot}

\newcommand{\ds}{\displaystyle}
\newcommand{\bv}{\mathbf}
\newcommand{\lv}{\langle}
\newcommand{\rv}{\rangle}

\begin{document}
\flushleft
\begin{multicols}{2}


\begin{large}\textbf{Math 116 Quiz 0: Student Guide \\
Fri 7 Sep 2012}\end{large}

\textbf{Name:  }\underline{\hspace{35ex}}

\vspace{.5in}

\end{multicols}

\pagestyle{empty}


\flushleft

Decide whether each of the statements below is \emph{True} or \emph{False}.  Write the entire word \emph{True} or \emph{False}.  If the statement is false, briefly explain why.  


\begin{enumerate}
\item  Math 116 is graded on a normal 10-point scale, that is 90-100=A, 80-90=B, etc.  
\vfill
\item  In general, a student should expect to do well in this course if he/she completes all assignments, reads each section before class, and puts in 3-4 hours of study time a week.
\vfill
\item If a particular type of problem or concept is not discussed in class, then it will not be on the exam.
\vfill
\item In order to emphasize working as a team, it is sometimes ideal for each member of a team homework group to submit a different problem in compiling the whole assignment for submission.
\vfill
\item If you do not participate in team homework and quizzes, your course grade will be based solely on your exam scores and web homework.
\vfill
\item The section component of the course helps your instructor determine if your final grade may be altered by one third of a letter grade.  While there is the opportunity for your grade to be raised, you instructor is not allowed to use section component scores to justify lowering your final grade.
\vfill
\item As long as you do well (i.e., above the median) in the section component according to the guidelines you instructor has set, you are likely to get the one third letter grade boost at the end of the term. 
\vfill
\item You can only take the online practice gateway exams twice a day, so it is important you start studying early.
\vfill
\item The gateway component is worth 5\% of your grade, so the scores you get make a difference, however small, in your grade. 
\vfill
\item  At the end of the semester, every section of Math 116 will have the same number of A's, B's, etc.

\end{enumerate}
\end{document}


